Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-28 Tex/Old text/chapters/chapter02.tex
Thesis update

In this chapter we present some concepts related to the intersection of the two areas: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.

@@

Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification can be applied to any kind of systems (from simple ones to the complex ones)

>>>>

In this chapter we present some concepts related to the intersection of the two areas:  computer science methods used to solve electrical engineering problems, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.

@@

Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification method can be applied to any kind of systems (from simple ones to the complex ones)

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
Thesis update

At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were applied to solar PV systems. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.

@@

One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems; and a international network of researchers in model checking applied to electrical systems.

>>>>

At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.

@@

One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems.

### 2019-10-28 Tex/Old text/chapters/introduction.tex
Thesis update

Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique.

Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork.

>>>>

Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new method of PV systems validation.

Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect from fieldwork.
